Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-20 checking-executions.tex
small stuff

\subsection{Checking Data-Differentiated Sequential Executions}\label{ssec:seq_exec}

@@

\subsection{Checking Data-Differentiated Concurrent Executions}\label{ssec:conc_exec}

>>>>

\subsection{Characterizing Data-Differentiated Sequential Executions}\label{ssec:seq_exec}

@@

\subsection{Checking Linearizability of Data-Differentiated Concurrent Executions}\label{ssec:conc_exec}
